---
output: github_document
---

## **censCov**

[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![minimal R version](https://img.shields.io/badge/R%3E%3D-3.4.0-6666ff.svg)](https://cran.r-project.org/)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/reReg)](https://cran.r-project.org/package=reReg)
[![packageversion](https://img.shields.io/badge/Package%20version-1.0.1-orange.svg?style=flat-square)](commits/master)
[![Travis-CI Build Status](https://travis-ci.org/stc04003/censCov.svg?branch=master)](https://travis-ci.org/stc04003/censCov)
[![Last-changedate](https://img.shields.io/badge/last%20change-2019--05--18-yellowgreen.svg)](/commits/master)

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

### Linear Regression with a Randomly Censored Covariate
***censCov*** consists of implementations of threshold regression approaches for linear regression models with a covariate subject to random censoring, including deletion threshold regression and completion threshold regression. Reverse survival regression, which flip the role of response variable and the covariate, is also considered.

### Installation

You can install and load **censCov** from CRAN using

```{r cran-installation, eval = FALSE}
install.packages("censCov")
library(censCov)
```

You can install `censCov` from github with:

```{r gh-installation, eval = FALSE}
## install.packages("devtools")
devtools::install_github("stc04003/censCov")
```

### Getting Started
The package [vignette](https://www.sychiou.com/censCov/index.html) provides a quick demonstration for the basic usage of the main functions.

### References:

  Qian, J., Chiou, S.H., Maye, J.E., Atem, F., Johnson, K.A. and Betensky, R.A. (2018).
  Threshold regression to accommodate a censored covariate, *Biometrics*, **74**(4):
  1261--1270.

  Atem, F., Qian, J., Maye J.E., Johnson, K.A. and Betensky, R.A. (2017),
  Linear regression with a randomly censored covariate: Application to an Alzheimer's study.
  *Journal of the Royal Statistical Society: Series C*, **66**(2):313--328.